Dusty Days and a Vibrio Craze: The Influence of Saharan Dust Deposition on Microbial Communities in High Nutrient Coastal Waters 

### 2023-05-06 code/analysis_code/dust/daily_dusts.qmd
Final Edits
After double checking manuscript, I noticed that figure proportions were off. (small text etc). I went back and readjusted but am wondering why I am just now noticing this. I am working on my laptop (as opposed to my desktop), so i am wondering if R is somehow correcting for screen resolution, and I am seeing different sized plots due to this. Please let me know if my figures look off when you review, thanks!

```{r}
dust<-
  dust %>%
  filter(date %in% as.Date('2022-07-07') : as.Date('2022-07-19'))
```

@@

```{r}
dust %>% ggplot()+ geom_line(
  aes(x = date,
      y = t7sum))+
  labs(title = "Dust Concentration over Daily Time Series",
       x = "Date",
       y = "Dust Concentration (AOD)")+
  theme_bw()
```

>>>>

```{r}
dust<-
  dust %>%
  filter(date %in% as.Date('2022-07-01') : as.Date('2022-07-31'))
```

@@

```{r}
dust %>% ggplot()+ geom_line(
  aes(x = date,
      y = t7sum))+
  labs(title = "Dust Concentration over Daily Time Series",
       x = "Date",
       y = "Dust Concentration (AOD)")+
  theme_bw()

ggsave(here("results", "plots", "dust_july.png"))
```

### 2023-05-06 code/analysis_code/environment/env_par.qmd
Final Edits
After double checking manuscript, I noticed that figure proportions were off. (small text etc). I went back and readjusted but am wondering why I am just now noticing this. I am working on my laptop (as opposed to my desktop), so i am wondering if R is somehow correcting for screen resolution, and I am seeing different sized plots due to this. Please let me know if my figures look off when you review, thanks!

```{r, fig.width= 8, fig.height=4}
fig<- ggarrange(temp,
                sal,
                #do,
                nn,
                ortho,
                don,
                doc,
                #pH,
                #amm,
                #tn,
                #sil,
                #cop,
                tdn,
                #secchi,
                #din,
                #din_dip,
                chl,
                ncol = 4, 
                nrow = 2,
                align = "v")

fig
```

# Save as PNG

```{r}
png(file = here("results", "plots", "temp_sal.png"))
fig
dev.off()
```

>>>>

```{r}
fig<- ggarrange(temp,
                sal,
                #do,
                nn,
                ortho,
                don,
                doc,
                #pH,
                #amm,
                #tn,
                #sil,
                #cop,
                tdn,
                #secchi,
                #din,
                #din_dip,
                chl,
                ncol = 4, 
                nrow = 2,
                align = "v")

fig

ggsave(here("results", "plots", "env.png"))
```

#

### 2023-05-06 products/manuscript/Manuscript.qmd
Final Edits
After double checking manuscript, I noticed that figure proportions were off. (small text etc). I went back and readjusted but am wondering why I am just now noticing this. I am working on my laptop (as opposed to my desktop), so i am wondering if R is somehow correcting for screen resolution, and I am seeing different sized plots due to this. Please let me know if my figures look off when you review, thanks!

Density and Q-Q plots as well as Shapiro-Wilk's tests were conducted to assess distribution of the data. Any data that did not have a normal distribution was log-transformed and the test was run again. Variables that continue to fail normality will have non-parametric tests run on them. <!--# Add more details about visualization -->

@@

CCF plots (found in supplemtary scripts) showed that BO has a significant lag relationship a value of -1. In other words, dust occurs, and one day later, we see a response in *Vibrio* gene copies per mL. C2 has a lag at -2, and RD at -1.

>>>>

Density and Q-Q plots as well as Shapiro-Wilk's tests were conducted to assess distribution of the data (SI). Any data that did not have a normal distribution was log-transformed and the test was run again. Variables that continue to fail normality will have non-parametric tests run on them. <!--# Add more details about visualization -->

@@

CCF plots (found in supplementary file) showed that BO has a significant lag relationship a value of -1. In other words, dust occurs, and one day later, we see a response in *Vibrio* gene copies per mL. C2 has a lag at -2, and RD at -1.
